---
title: "Bricks"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Bricks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo=FALSE}
library(sits.prodes)
```

## Interpolated bricks (original).

These bricks are made of Landsat 8 SR and MOD13Q1 images. The clouds in the 
Landsat images were filled up using data bilinear interpolation of MXD13 
images. For each image, vegetation indexes were computed and assembled into 
bricks, which makes these bricks inconsistent with those computed directly from 
the band bricks. 

* Location: "cronos:/dados1/Repository/Brick/LC8/LC8SR-MOD13Q1-MYD13Q1"
* Scenes: 221068, 221069, 221070, 225063, 226064, 232066, 233067.
* Years: 2013, 2014, 2015, 2016.
* Bands: blue, evi, ndvi, nir, red, swir2.
* Bands per brick: 23.


## Interpolated bricks (new).

These bricks are made of Landsat 8 SR and MOD13Q1 images. The clouds in the 
Landsat images were filled up using data bilinear interpolation of MXD13 
images. The vegetation index bricks were computed from the band bricks, ensuring 
consitency. Besides, dubious EVI bricks were removed do to inconsistencies on 
vegetation index definition between Landsat and MODIS.

* Location: "esensing-006:/disks/d6/shared/alber/brick_interp"
* Scenes: 225063, 226064, 233067, .
* Years: 2013, 2014, 2015, 2016.
* Bands: ndvi, nir, red, swir2.
* Bands per brick: 23.



## StarFM bricks.

These bricks are made of Landsat 8 SR and MOD13Q1 images. The clouds in the 
Landsat8 images were filled up using the StarFM mixture model. The vegetation 
index bricks were computed from the band bricks.

* Location: "esensing-006:/disks/d6/shared/alber/brick"
* Scenes: 225063, 226064, 233067, .
* Years: 2013, 2014, 2015 (not for all), 2016.
* Bands: ndvi, nir, red, swir2.
* Bands per brick: 23.



## StarFM bricks (few clouds).

These bricks are made of Landsat 8 SR and MOD13Q1 images with the fewer clouds at 
the start and end of the PRODES year (from August to July). The clouds in the 
Landsat8 images were filled up using the StarFM mixture model. The vegetation 
index bricks were computed from the band bricks.

* Location: "esensing-006:/disks/d6/shared/alber/brick_interp_few_clouds"
* Scenes: 225063.
* Years: 2014, 2016 (incomplete).
* Bands: blue, nir, red, swir2 (incomplete).
* Bands per brick: 4.



## Simple bricks.

These bricks are made of Landsat 8 SR with the fewer clouds at the start and end 
of the PRODES year (from August to July).

* Location:  "esensing-006:/disks/d6/shared/alber/brick_simple"
* Scenes: 225063, 226064, 233067, .
* Years: 2013, 2014, 2015, 2016.
* Bands: blue, dark, ndvi, nir, red, substrate, swir2, vegetation.
* Bands per brick: 4.


## Mask cloud bricks.

These bricks are made of Landsat 8 SR with masked clouds. They include 
vegetation indexes, and spectral mixture models.

* Location: "esensing-006:/disks/d6/shared/alber/brick_maskcloud"
* Scenes: 225063, 226064, 233067.
* Years: 2013, 2014, 2015, 2016.
* Bands: blue, green, nir, red, swir1, swir2, dark, substrate, vegetation, ndvi, cloud.
* Bands per brick: 4.



## Raw bricks.

These bricks are made of Landsat 8 SR images.

* Location: "esensing-006:/disks/d6/shared/alber/brick_raw"
* Scenes: 225063, 226064, 233067.
* Years: 2013, 2014, 2015, 2016.
* Bands: blue, cloud, dark, ndvi, nir, red, substrate, swir2, vegetation.
* Bands per brick: 23.



## TODO

* Missing StarFM bricks for some scenes in 2015.
* brick_interp_few_clouds got the name wrong, it shoudl be brick_starfm_few_clouds.
* Some MASK_CLOUD bricks are mixtured with SIMPLE.
* /disks/d6/shared/alber/brick_maskcloud clouds' date is one day before the rest of the bricks. 
